Air Quality and CMS Data

### 2021-01-25 code/data-processors/air-data-processor.Rmd
import different buffersize cms data add indentation

dt.aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
  filter(
    #remove monitors closed before 2000
    year(as.Date(Site.Closed.Date)) >= 2000 | Site.Closed.Date == "",
    !State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
                       "Guam", "Country Of Mexico","Canada") #remove non-CONUS states
    ) %>%  
  transmute(
    Site.ID = as.factor(sprintf("%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
                                as.numeric(as.character(State.Code)),
                                County.Code, Site.Number)), 
    State.Code = as.factor(sprintf("%02d", as.numeric(as.character(State.Code)))),
    County.Code = as.factor(sprintf("%03d", County.Code)),
    Latitude,
    Longitude, 
    State = state.abb[match(State.Name,state.name)],
    State = as.factor(ifelse(State.Name == "District Of Columbia","DC", State)),
    Land.Use,
    Location.Setting = as.factor(ifelse(Location.Setting == "URBAN AND CENTER CITY",
                                        "URBAN",
                                        as.character(Location.Setting)))
    ) %>% 
  merge(dt.state.region[, c("State", "Region.IV")]) %>% 
  arrange(Site.ID)

@@

```{r IMPROVE Data cleaning}
# EC 88307 -> TOT
# OC 88320 -> TOR
dt.imprv.raw = data.frame()
for (i in seq(2000,2008,1)){
  dt0 <- read.delim(here('data','raw','improve',paste0('improve_',i,'.txt')), sep = ',')
  dt.imprv.raw <- rbind(dt.imprv.raw, dt0)
}
colnames(dt.imprv.raw) <- colnames(dt.imprv.raw) %>% str_remove("f.Value")

@@

# find the diff bw spec & improve
monitor.spec <- dt.spec.w %>% distinct(Monitor.ID) #659
monitor.imprv <- dt.imprv.raw %>% distinct(Monitor.ID) #189
monitor.diff.imprv <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID) %>% 
  as.data.frame() #32
colnames(monitor.diff.imprv) <- 'Monitor.ID'
# improve has 32 Monitor.ID that spec does not have

@@

# site-close-zip-pmc.csv was uploaded on NEU Cluster to be merged with daily zipcode level
# ... PM data.

>>>>

dt.aqs.sites <- read.csv(unz(temp,"aqs_sites.csv")) %>%
  filter(
    #remove monitors closed before 2000
    year(as.Date(Site.Closed.Date)) >= 2000 | Site.Closed.Date == "",
    !State.Name %in% c("Alaska","Hawaii","Puerto Rico","Virgin Islands",
                       "Guam", "Country Of Mexico","Canada") 
    #remove non-CONUS states
    ) %>%  
  transmute(
    Site.ID = as.factor(sprintf(
      "%02d-%03d-%04d", #unique ID for each Site: ss-ccc-nnnn
                                as.numeric(as.character(State.Code)),
                                County.Code, Site.Number)), 
    State.Code = as.factor(sprintf("%02d", as.numeric(as.character(State.Code)))),
    County.Code = as.factor(sprintf("%03d", County.Code)),
    Latitude,
    Longitude, 
    State = state.abb[match(State.Name,state.name)],
    State = as.factor(ifelse(State.Name == "District Of Columbia","DC", State)),
    Land.Use,
    Location.Setting = as.factor(
      ifelse(Location.Setting == "URBAN AND CENTER CITY", "URBAN",
             as.character(Location.Setting)))
    ) %>% 
  merge(dt.state.region[, c("State", "Region.IV")]) %>% 
  arrange(Site.ID)

@@

```{r IMPROVE Data cleaning}
# EC 88307 -> TOT
# OC 88320 -> TOR
dt.imprv.raw = data.frame()
for (i in seq(2000,2008,1)){
  dt0 <- read.delim(
    here('data','raw','improve',paste0('improve_',i,'.txt')), sep = ',')
  dt.imprv.raw <- rbind(dt.imprv.raw, dt0)
}
colnames(dt.imprv.raw) <- colnames(dt.imprv.raw) %>% str_remove("f.Value")

@@

# find the diff bw spec & improve
monitor.spec <- dt.spec.w %>% distinct(Monitor.ID) #659
monitor.imprv <- dt.imprv.raw %>% distinct(Monitor.ID) #189
monitor.diff.imprv <- setdiff(monitor.imprv$Monitor.ID, monitor.spec$Monitor.ID
                              ) %>% 
  as.data.frame() #32
colnames(monitor.diff.imprv) <- 'Monitor.ID'
# improve has 32 Monitor.ID that spec does not have

@@

# site-close-zip-pmc.csv was uploaded on NEU Cluster to be merged with ...
# ... daily zipcode level PM data.

### 2021-01-25 code/data-processors/cms-data-processor.Rmd
import different buffersize cms data add indentation

```{r Import and save CMS(/ndi) data}
dt.master.ndi.pmc <- read.csv(here('data', 'processed','master_ndi_pmc.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc, file = here('data', 'processed', 'master-ndi-pmc.RDa'))

dt.master.ndi.pmc.race <- read.csv(here('data', 'processed','master_ndi_pmc_race.csv')) %>%
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.race, file = here('data', 'processed', 'master-ndi-pmc-race.RDa'))

dt.master.ndi.pmc.bz6 <- read.csv(here('data', 'processed','master_ndi_pmc_bz6.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.bz6, file = here('data', 'processed', 'master-ndi-pmc-bz6.RDa'))

dt.master.ndi.pmc.bz12 <- read.csv(here('data', 'processed','master_ndi_pmc_bz12.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.bz12, file = here('data', 'processed', 'master-ndi-pmc-bz12.RDa'))

dt.master.ndi.pmc.bz24 <- read.csv(here('data', 'processed','master_ndi_pmc_bz24.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.bz24, file = here('data', 'processed', 'master-ndi-pmc-bz24.RDa'))
```

@@

```{r PMC - 4yr}
dt.pmc <- dt.pmc.4yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC - 3yr}
dt.pmc <- dt.pmc.3yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC - 2yr}
dt.pmc <- dt.pmc.2yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC - 1yr}
dt.pmc <- dt.pmc.1yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

>>>>

```{r Import and save CMS(/ndi) data}
# bz = 12
dt.master.ndi.pmc <- read.csv(
  here('data', 'processed','master_ndi_pmc.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc, 
     file = here('data', 'processed', 'master-ndi-pmc.RDa'))

# bz =12 - race
dt.master.ndi.pmc.race <- read.csv(
  here('data', 'processed','master_ndi_pmc_race.csv')) %>%
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.race, 
     file = here('data', 'processed', 'master-ndi-pmc-race.RDa'))

# bz = 6
dt.master.ndi.pmc.bz6 <- read.csv(
  here('data', 'processed','master_ndi_pmc_bz6.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.bz6, 
     file = here('data', 'processed', 'master-ndi-pmc-bz6.RDa'))

# bz = 12 of sites of bz =6
dt.master.ndi.pmc.bz12 <- read.csv(
  here('data', 'processed','master_ndi_pmc_bz12.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.bz12, 
     file = here('data', 'processed', 'master-ndi-pmc-bz12.RDa'))

# bz = 24 of sites of bz =6
dt.master.ndi.pmc.bz24 <- read.csv(
  here('data', 'processed','master_ndi_pmc_bz24.csv')) %>% 
  rename(Site.ID = Site_ID,
         Year = year,
         Month = MONTH,
         age = ENROLLEE_AGE)
save(dt.master.ndi.pmc.bz24, 
     file = here('data', 'processed', 'master-ndi-pmc-bz24.RDa'))
```

@@

```{r PMC - 4yr - 5yr}
dt.pmc <- dt.pmc.4yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC - 3yr - 5yr}
dt.pmc <- dt.pmc.3yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC - 2yr - 5yr}
dt.pmc <- dt.pmc.2yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC - 1yr - 5yr}
dt.pmc <- dt.pmc.1yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))
